R Course Syllabus

### 2023-05-02 Bookdown Syllabus/Bookdown Syllabus.Rmd
Minor updates to lesson 4; include additional link and fix typo

Providing multiple columns to arrange will break ties on using succeeding columns:

@@

* [Codecademy Lesson Pt. 1](https://www.codecademy.com/courses/learn-r/lessons/r-data-frames-intro/exercises/introduction)
* [Codecademy Lesson Pt. 2](https://www.codecademy.com/courses/learn-r/lessons/r-data-frames-modifying/exercises/introduction)
* [More about dplyr](https://dplyr.tidyverse.org/)

>>>>

Providing multiple columns to arrange will break ties using succeeding columns:

@@

* [Codecademy Lesson Pt. 1](https://www.codecademy.com/courses/learn-r/lessons/r-data-frames-intro/exercises/introduction)
* [Codecademy Lesson Pt. 2](https://www.codecademy.com/courses/learn-r/lessons/r-data-frames-modifying/exercises/introduction)
* [More about dplyr](https://dplyr.tidyverse.org/)
* [dplyr function cheat sheet](https://dplyr.tidyverse.org/reference/index.html)
